---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description}
# Describe your package
fusen::fill_description(
  fields = list(
    Title = "Create a kniting image from an image",
    Description = "From any image, creation of an image to knit a rectangle representing the simplified image and a summary table of colors and number of stitches according to the chosen needles.",
    `Authors@R` = c(
      person("Marie", "Vaugoyeau", email = "marie.vaugoyeau@gmail.com", role = c("aut", "cre")),
      person(given = "MStats", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Marie Vaugoyeau")
```
  
  
# Load image  

```{r function}

#' Load image
#'
#' @param path Path to load image
#' @inheritParams magick::image_read 
#' @inheritParams stringr::str_detect
#'
#' @return
#' Magick image in R
#' @export
#'
#' @examples
image_load <- function(path) {
  if (!file.exists(path)) {stop("path is incorrect")}
  
  if (sum(stringr::str_detect(path, c(".jpeg", ".jpg", ".png", ".tif"))) > 0) {magick::image_read(path)}
  else if (stringr::str_detect(path, ".pdf")) {magick::image_read_pdf(path, pages = 1)}
  else {stop("format is not supported")}
}

```
  
```{r examples}
image_load("img/PeintureLaetitia.jpg")
image_load("img/Montagne.pdf")
image_load("img/Pingouin.png")
image_load("img/Monstre.tif")
```

```{r tests}
test_that("load image and show error if needed", {
  expect_true(class(image_load("img/PeintureLaetitia.jpg")) == "magick-image")
  expect_error(image_load("text"))
})
```

# Calculate the size of square based on the information provided on the label   
  
Normally on the balls of wool there is the information to knit a square of 10 x 10 cm.
  
```{r function-1}

#' Load image
#'
#' @param rg Row number to have 10 cm
#' @param m Stitch number to have 10 cm
#'
#' @return
#' Square size to do grid on image
#' @export
#'
#' @examples
square_size <- function(rg, m) {
  if (!is.numeric(rg)) {stop("rg should be numeric")}
  if (!is.numeric(m)) {stop("m should be numeric")}
  
  c(
    height = round(10/rg, 3),
    width = round(10/m, 3)
  )
}

```
  
```{r examples-1}
square_size(31,24)
square_size(35,26)
```

```{r tests-1}
test_that("calcule square size and show error if needed", {
  expect_true(sum(square_size(31,24) == c(height = 0.323, width = 0.417)) == 2)
  expect_error(square_size("text"))
})
```

  

STOP, je me suis arrêtée là !


# Calculate the median of a vector

```{r function}
#' My median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

```{r examples}
my_median(1:12)
```

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})
```

# Calculate the mean of a vector
## Use sub-functions in the same chunk

```{r function-1}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-1}
my_other_median(1:12)
```

```{r tests-1}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

