---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description}
# Describe your package
fusen::fill_description(
  fields = list(
    Title = "Create a kniting image from an image",
    Description = "From any image, creation of an image to knit a rectangle representing the simplified image and a summary table of colors and number of stitches according to the chosen needles.",
    `Authors@R` = c(
      person("Marie", "Vaugoyeau", email = "marie.vaugoyeau@gmail.com", role = c("aut", "cre")),
      person(given = "MStats", role = "cph")
    )
  ),
  overwrite = TRUE
)
# Define License with use_*_license()
usethis::use_mit_license("Marie Vaugoyeau")
```
  
  
# Load image  

```{r function}

#' Load image
#'
#' @param path Path to load image
#' @inheritParams magick::image_read 
#' @inheritParams stringr::str_detect
#'
#' @return
#' Magick image in R
#' @export
#'
#' @examples
image_load <- function(path) {
  if (!file.exists(path)) {stop("path is incorrect")}
  
  if (sum(stringr::str_detect(path, c(".jpeg", ".jpg", ".png", ".tif"))) > 0) {magick::image_read(path)}
  else if (stringr::str_detect(path, ".pdf")) {magick::image_read_pdf(path, pages = 1)}
  else {stop("format is not supported")}
}

```
  
```{r examples}
tricot::image_load("img/PeintureLaetitia.jpg")
tricot::image_load("img/Montagne.pdf")
tricot::image_load("img/Pingouin.png")
tricot::image_load("img/Monstre.tif")
```

```{r tests}
test_that("load image and show error if needed", {
  expect_true(class(tricot::image_load("img/PeintureLaetitia.jpg")) == "magick-image")
  expect_error(tricot::image_load("text"))
})
```
  
  
  
# Square size calculation based on the information provided on the label   
  
Normally on the balls of wool there is the information to knit a square of 10 x 10 cm.
  
```{r function-1}

#' Square of size
#'
#' @param rg Row number to have 10 cm
#' @param m Stitch number to have 10 cm
#'
#' @return
#' Square size to do grid on image
#' @export
#'
#' @examples
square_size <- function(rg, m) {
  if (!is.numeric(rg)) {stop("rg should be numeric")}
  if (length(rg) != 1) {stop("rg should have only one value")}
  if (!is.numeric(m)) {stop("m should be numeric")}
  if (length(m) != 1) {stop("m should have only one value")}
  
  c(
    height = round(10/rg, 3),
    width = round(10/m, 3)
  )
}

```
  
```{r examples-1}
tricot::square_size(31,24)
tricot::square_size(35,26)
```

```{r tests-1}
test_that("calcule square size and show error if needed", {
  expect_true(sum(tricot::square_size(31,24) == c(height = 0.323, width = 0.417)) == 2)
  expect_error(tricot::square_size("text"))
})
```
  
  
# Gride size calculation from expected height and width   
  
Calculation of the pixel size according to the size of the row and the previously given stitch and with the size of the knit you are looking for.  
  
```{r function-2}

#' Grid size
#'
#' @param h Expected height (cm) of knitting
#' @param w Expected width (cm) of knitting
#' @param ss Size square calculated from square_size()
#'
#' @return
#' Grid size to do grid on image
#' @export
#'
#' @examples
grid_size <- function(h, w, ss) {
  if (!is.numeric(h)) {stop("h should be numeric")}
  if (length(h) != 1) {stop("h should have only one value")}
  if (!is.numeric(w)) {stop("w should be numeric")}
  if (length(w) != 1) {stop("w should have only one value")}
  if (!is.numeric(ss)) {stop("gs should be numeric")}
  if (length(ss) != 2) {stop("gs should have only two values")}
  
  c(
    grid = ceiling(h/ss["height"]),
    grid = ceiling(w/ss["width"])
  )
}

```
  
```{r examples-2}
tricot::grid_size(20, 20, square_size(31,24)) 
tricot::grid_size(5, 5, square_size(35,26))
```

```{r tests-2}
test_that("calcule grid size and show error if needed", {
  expect_true(sum(tricot::grid_size(5, 5, tricot::square_size(35,26)) == c(grid.height = 18, grid.width = 13)) == 2)
  expect_error(tricot::square_size("text"))
})
```
  
  
# Image to knit       
  
In Shiny app, knitting image will show with plotly `plotly::ggplotly()`.  
  
```{r function-3}

#' Creation of knitting image
#'
#' @param img Magick image
#' @param gs Grid size calculated from grid_size()
#' @inheritParams dplyr::arrange 
#' @inheritParams magick::image_raster
#' @inheritParams magick::image_scale
#' @inheritParams ggplot2::ggplot
#' @inheritParams ggplot2::aes
#' @inheritParams ggplot2::geom_point
#' @inheritParams ggplot2::scale_color_manual
#' @inheritParams dplyr::distinct
#' @inheritParams ggplot2::theme
#' @inheritParams ggplot2::xlab
#' @inheritParams ggplot2::ylab
#'
#' @return
#' Knitting image
#' @export
#'
#' @examples
knitting_image <- function(img, gs) {
  
  if(class(img) != "magick-image") {stop("img must be magick image")}
  if (!is.numeric(gs)) {stop("gs should be numeric")}
  if (length(gs) != 2) {stop("gs should have only two values")}

  raster_image <- 
    dplyr::arrange(
      magick::image_raster(
        magick::image_scale(
          img, 
          glue::glue('{gs["grid.width"]}x{gs["grid.height"]}!'))
        ), 
      col
      )
    
    
  kimage <- ggplot2::ggplot(raster_image) + 
    ggplot2::aes(x = x, y = max(y) + 1 - y, color = col) + 
    ggplot2::geom_point(shape = 15) + 
    ggplot2::scale_color_manual(values = dplyr::distinct(raster_image, col)$col) + 
    ggplot2::theme(
      legend.position = "none", 
      panel.background = ggplot2::element_blank(),
      panel.grid.major = ggplot2::element_line(colour = "black"),
      panel.grid.minor = ggplot2::element_line(colour = "grey")
    ) +
    ggplot2::xlab("maille") +
    ggplot2::ylab("rang")
    
  return(kimage)
  
}

```
  
```{r examples-3}

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Montagne.pdf")
    ), 
  tricot::grid_size(
    20, 
    30, 
    tricot::square_size(
      35,
      26
    )
    )
  )

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Monstre.tif")
    ), 
  tricot::grid_size(
    30, 
    30, 
    tricot::square_size(
      35,
      26
    )
    )
  )

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Pingouin.png")
    ), 
  tricot::grid_size(
    20, 
    20, 
    tricot::square_size(
      35,
      26
    )
    )
  )

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "PeintureLaetitia.jpg")
    ), 
  tricot::grid_size(
    30, 
    20, 
    tricot::square_size(
      35,
      26
    )
    )
  )

```

```{r tests-3}
test_that(
  "calcule knitting image", 
  {
    expect_true(
      sum(
        class(
          tricot::knitting_image(
            tricot::image_load("img/Pingouin.png"), 
            c("grid.height" = 31, "grid.width" = 24)
          )
        ) == "ggplot"
      ) > 0)
    expect_error(tricot::knitting_image("text"))
  })

```
  
  
  
# Wool needed calclulation           
  
```{r function-4}

#' Calculation of the wool quantity needed
#'
#' @param img_k ggplot image from knitting_image()
#' @param rg Row number to have 10 cm
#' @param m Stitch number to have 10 cm
#' @param p Weight (g) to make the test square of 10*10
#' @inheritParams dplyr::arrange 
#' @inheritParams magick::image_raster
#' @inheritParams magick::image_scale
#' @inheritParams ggplot2::ggplot
#' @inheritParams ggplot2::aes
#' @inheritParams ggplot2::geom_point
#' @inheritParams ggplot2::scale_color_manual
#' @inheritParams dplyr::distinct
#' @inheritParams ggplot2::theme
#' @inheritParams ggplot2::xlab
#' @inheritParams ggplot2::ylab
#'
#' @return
#' Table with wool weight needed by color
#' @export
#'
#' @examples
wool_weigth_needed <- function(img_k, rg, m, p) {
  
  if(sum(class(img_k) != "ggplot") == 0) {stop("img_k must be ggplot")}
  if (!is.numeric(rg)) {stop("rg should be numeric")}
  if (length(rg) != 1) {stop("rg should have only one value")}
  if (!is.numeric(m)) {stop("m should be numeric")}
  if (length(m) != 1) {stop("m should have only one value")}
  if (!is.numeric(p)) {stop("p should be numeric")}
  if (length(p) != 1) {stop("p should have only one value")}
  
  table <- dplyr::mutate(
        dplyr::count(
          img_k$data, 
          col
        ),
        "wool_needed (g)" = round(n * p / (rg * m), digits = 2)
      )
  
  table_couleur <-
    DT::formatStyle(
      DT::datatable(
        table,
        rownames = FALSE
        ),
      "col",
      backgroundColor = 
        DT::styleEqual(
          dplyr::distinct(table, col)$col,
          dplyr::distinct(table, col)$col
        )
    )
  
  return(table_couleur)
}

```
  
```{r examples-4}

tricot::wool_weigth_needed(
  tricot::knitting_image(
  tricot::image_load(
    "img/Montagne.pdf"
    ), 
  tricot::grid_size(
    20, 
    30, 
    tricot::square_size(
      35,
      26
    )
    )
  ),
  35,
  26,
  100
)

```

```{r tests-4}
test_that(
  "calcule knitting image", 
  {
    expect_true(
      sum(
        class(
          tricot::wool_weigth_needed(
            tricot::knitting_image(
              tricot::image_load(
                "img/Pingouin.png"
              ), 
              tricot::grid_size(
                30, 
                30, 
                tricot::square_size(
                  35,
                  26
                )
              )
            ),
            35,
            26,
            100
          )
        ) == "datatables"
      ) > 0)
    expect_error(tricot::wool_weigth_needed("text"))
  })

```  
  
  
  
# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

