---
title: "exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tricot)
```

<!--

# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 


  
  

# Load image  

  

```{r examples}
tricot::image_load(here::here("img", "PeintureLaetitia.jpg"))
tricot::image_load(here::here("img", "Montagne.pdf"))
tricot::image_load(here::here("img", "Pingouin.png"))
tricot::image_load(here::here("img", "Monstre.tif"))
```

  
  
  

# Square size calculation based on the information provided on the label   

  
Normally on the balls of wool there is the information to knit a square of 10 x 10 cm.
  

  

```{r examples-1}
tricot::square_size(31,24)
tricot::square_size(35,26)
```

  
  

# Gride size calculation from expected height and width   

  
Calculation of the pixel size according to the size of the row and the previously given stitch and with the size of the knit you are looking for.  
  

  

```{r examples-2}
tricot::grid_size(20, 20, square_size(31,24)) 
tricot::grid_size(5, 5, square_size(35,26))
```

  
  

# Image to knit       

  
In Shiny app, knitting image will show with plotly `plotly::ggplotly()`.  
  

  

```{r examples-3}

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Montagne.pdf")
    ), 
  tricot::grid_size(
    20, 
    30, 
    tricot::square_size(
      35,
      26
    )
    )
  )

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Monstre.tif")
    ), 
  tricot::grid_size(
    30, 
    30, 
    tricot::square_size(
      35,
      26
    )
    )
  )

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Pingouin.png")
    ), 
  tricot::grid_size(
    20, 
    20, 
    tricot::square_size(
      35,
      26
    )
    )
  )

tricot::knitting_image(
  tricot::image_load(
    here::here("img", "PeintureLaetitia.jpg")
    ), 
  tricot::grid_size(
    30, 
    20, 
    tricot::square_size(
      35,
      26
    )
    )
  )


```

  
  
  

# Wool needed calclulation           

  

  

```{r examples-4}

tricot::wool_weigth_needed(
  tricot::knitting_image(
  tricot::image_load(
    here::here("img", "Montagne.pdf")
    ), 
  tricot::grid_size(
    20, 
    30, 
    tricot::square_size(
      35,
      26
    )
    )
  ),
  35,
  26,
  100
)

```

  
  
  

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory


